\documentclass{cmspaper}
\usepackage{color}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{slashbox}
\usepackage{epstopdf}  %added for MAC compiler
\usepackage{pdfpages}
\usepackage{lineno}
\usepackage{verbatim}
\RequirePackage{lineno} 
%\RequirePackage{lineno} 

\usepackage{wrapfig}

%Note to authors: these definitions are suggested to be used for consistency
\newcommand{\pt}{$p_T$ }
\newcommand{\mll}{\ensuremath{M_{\ell\ell}}}
\newcommand{\z}{$Z$ }
\newcommand{\Z}{$Z$ } %redundancy can be good
\newcommand{\ttbar}{\ensuremath{t\bar{t}} }
\newcommand{\emu }{\ensuremath{e\mu}}
\newcommand{\ee  }{\ensuremath{ee}}
\newcommand{\eepm}{\ensuremath{e^+ e^-}}
\newcommand{\mm  }{\ensuremath{\mu\mu}}
\newcommand{\mmpm}{\ensuremath{\mu^+ \mu^-}}
\newcommand{\empm}{\ensuremath{e^\pm \mu^\mp}}
\newcommand{\ase}[2]{\ensuremath{_{~- #1}^{~+ #2}}}
\newcommand{\met}{\mbox{$\raisebox{.3ex}{$\not$}E_T$\hspace*{0.5ex}}} 
\newcommand{\effr}{$R_{e\mu}$} %used to be \epsilon
\newcommand{\sta}{$\sigma\times A$} %notation is such that A includes BR
\newcommand{\statistics}{CL$_\mathrm{S}$}

%The lumi so that if it changes it's easier to update
\newcommand{\lumi}{976~pb$^{-1}$}

%loose(tight) signal region met cut
\newcommand{\signalmetl}{100}
\newcommand{\signalmett}{200}

\newcommand{\resulttitle}
%{                      &   N(MET $>30$)  GeV    &   N(MET $>60$)  GeV    &   N(MET $>100$) GeV    &   N(MET $>200$) GeV \\}
{                       &   MET $>30$  GeV    &   MET $>60$  GeV    &   MET $>100$ GeV    &   MET $>200$ GeV \\}

%add this to captions (?)
%\newcommand{\oflw}{}

\begin{document}


\begin{titlepage}

  %\internalnote{2011/000}
  \cmsnote{2011/000}

  \date{\today}
 
  \title{A Search For New Physics in Z + Jets + MET using MET Templates}

  \begin{Authlist}
    D.~Barge, C.~Campagnari, P.~Kalavase, D.~Kovalskyi, V.~Krutelyov, V. Pavlunin, J.~Ribnik
    \Instfoot{ucsb}{University of California, Santa Barbara, USA}

    W.~Andrews, G.~Cerati, D.~Evans, F.~Golf, I.~MacNeill, S.~Padhi, Y.~Tu, F.~W\"urthwein, 
	A.~Yagil, J.~Yoo
    \Instfoot{ucsd}{University of California, San Diego, USA}

	L.~Bauerdick, I.~Bloch, K.~Burkett, I.~Fisk, Y.~Gao, O.~Gutsche, B.~Hooberman, 
	S.~Jindariani, J.~Linacre
    \Instfoot{fnal}{Fermi National Accelerator Laboratory, Batavia, Illinois, USA}
  \end{Authlist}

  \begin{abstract}

\begin{comment}

We search for new physics in the dilepton final state of Z plus two or more jets plus 
missing transverse 
energy (MET) in the $\sqrt{s}$ = 7~TeV data in 2011 (976~pb$^{-1}$). 
The Z boson is reconstructed in its decay to $e^+e^-$ or $\mu^+\mu^-$, and
the search regions are defined as MET $\ge$ 100 GeV (loose signal region) and 
MET $\ge$ 200 GeV (tight signal region). 
We use data driven techniques to predict the standard model background in these
search regions. 
Contributions from Drell-Yan production combined with detector mis-measurements that produce
fake MET are modeled via MET templates.
Top pair production background, as well as other backgrounds for which the lepton
flavors are uncorrelated, are modeled via $e^\pm\mu^\mp$ subtraction.
We find no evidence
for anomalous yield beyond SM expectations and place upper limits
on the non SM yields in the signal regions
and model dependent limits on LM4 and LM8 which show that LM4 is ruled out.

\end{comment}

%Above for upload

We search for new physics in the dilepton final state of \Z plus two or more jets plus 
missing transverse 
energy (MET) in the $\sqrt{s}$ = 7~TeV data in 2011 (\lumi). 
The \Z boson is reconstructed in its decay to $e^+e^-$ or $\mu^+\mu^-$, and
the search regions are defined as MET $\ge$ \signalmetl~GeV (loose signal region) and 
MET $\ge$ \signalmett~GeV (tight signal region). 
We use data driven techniques to predict the standard model background in these
search regions. 
Contributions from Drell-Yan production combined with detector mis-measurements that produce
fake MET are modeled via MET templates.
Top pair production background, as well as other backgrounds for which the lepton
flavors are uncorrelated, are modeled via $e^\pm\mu^\mp$ subtraction.
We find no evidence
for anomalous yield beyond SM expectations and place upper limits
on the non SM yields in the signal regions 
and model dependent limits on LM4 and LM8 which show that LM4 is ruled out.


  \end{abstract}
\end{titlepage}


\setcounter{page}{2}%JPP


\newpage
\tableofcontents

\newpage
\linenumbers
\input{introduction.tex}
\input{datasets.tex}
\input{eventsel.tex}
\input{yields.tex}
\input{sigregion.tex}
\clearpage

\input{templateintro.tex}
\input{templatemc.tex}
\clearpage

\input{topbkg.tex}
\input{otherBG}
\input{results.tex}
\clearpage

%syst on bkgnd preds
\input{systematics.tex}

%UL on non-SM yeild
\input{upperlimit}

%Additional Information for Model Testing
\input{outreach}

%model-dependent limits
\clearpage
\input{models.tex}
%\clearpage
\input{conclusion}

\clearpage
\input{bibliography.tex}

\clearpage
\appendix
\input{triggersdetails}
\clearpage
\input{appendix_em.tex}
\clearpage
\input{appendix_sigevts.tex}
\clearpage
\input{appendix_templates.tex}

\end{document}



