\section{Changes w.r.t. previous AN Version}
\label{sec:changes}

\begin{itemize}

\item v11: Updated the results of the targeted analysis by applying the b-veto to the MC background prediction and fixing the MC statistical uncertainty
in the highest \MET\ bin. See Fig.~\ref{fig:results_targ} and Table~\ref{tab:results_targ}.
\item v10: For targeted analysis, added plot of dilepton mass after the signal region \MET\ requirement (see Fig.~\ref{fig:results_targ}). Also applied method to the high dijet mass control region (see Fig.~\ref{fig:results_targ_control} and Table~\ref{tab:results_targ_control}).
\item v9: Added description of signal efficiency uncertainties (Sec.~\ref{sec:syst}). 
Added detailed summary of systematic uncertainties in the \MET\ templates prediction (Sec.~\ref{sec:bkg_zjetssyst}), including the MC closure study (App.~\ref{sec:templateclosure}).
Added plots requested by Petar in his review for the pre-approval. Cosmetic improvements to the targeted analysis ``money plot'' Fig.~\ref{fig:results_targ}, including
reduction of the (previously over-estimated) systematic uncertainty in the \MET\ $<$ 60 GeV region.
\item v8: Add studies of PU variable beta in App.~\ref{sec:pujets}. Small (few \%) change to \MET\ templates prediction from fixing issue related to prescalees of the single photon triggers.
\item v7: Add rejection of PU jets using the beta variable. Update the trigger efficiencies using measurements of the full 2012 sample. Update the data sample to the full 19.5 fb$^{-1}$. Correct the cross sections for the ZZZ and ZZJetsTo2L2Q MC samples.
\item v6: Updated experimental results based on full 2012 sample, corresponding to 19.3 fb$^{-1}$.
\item v5: {\bf This is the version corresponding to the HCP results}. Added interpretation for the GMSB model. % (Sec.~\ref{sec:interpretation}. 
Added data vs. MC kinematic distributions for the sample with 3 leptons and at least 2 jets, where we observe an excess of data with respect to the MC prediction. % (App.~\ref{app:WZ}).
\item v4: Un-blinded the results of the inclusive and targeted analysis, and added an interpretation in the \wzmet\ model. Moved the material for the edge analysis to a separate AN (2012/359).
\item v3: Added results for the low-\MET\ and high-\MET\ signal regions used for the edge analysis, for the first 5.1 fb$^{-1}$ 2012A+B data.
\item v2: Updated to 9.2 fb$^{-1}$ of 53X data and MC (v1 used 5.1 fb$^{-1}$ 52X data and MC).

\end{itemize}
