\clearpage

\section{Datasets and Triggers}
\label{sec:datasets}

In this section we list the datasets, triggers, and MC samples used in the analysis. For selecting signal
events, we use dilepton triggers in the DoubleElectron, DoubleMu, and MuEG datasets. 
An event in the ee final state is required to pass the dielectron trigger, a 
$\mu\mu$ event is required to pass the dimuon trigger, while an e$\mu$ event is required to pass at least one 
of the two $e-\mu$ cross triggers. The efficiencies of the ee, $\mu\mu$ and e$\mu$ triggers with respect to the
offline selection have been measured as $0.95\pm0.03$, $0.88\pm0.03$, and $0.92\pm0.03$, respectively~\cite{ref:SSAN}.  
These trigger efficiencies were measured with the first 5.1 fb$^{-1}$ and will be updated with the full data sample. 
Preliminary measurements of the trigger efficiency with the full sample show consistent results within $\sim1-2$\%.
A sample of \gjets\ events, used as a control sample to estimate the \zjets\
background, is selected using a set of single photon triggers.
The golden json of Aug 31st, corresponding to an integrated luminosity of 9.7 fb$^{-1}$, is used as the starting point.
However, due to a bug in the Run2012C-PromptReco-v1 data samples (corresponding to 0.5 fb$^{-1}$), this portion of the data
is currently excluded but will be added back after it is reprocessed. Thus we currently use a sample corresponding to \lumi.
All data and MC samples are processed in CMSSW\_5\_3\_2\_patch4.

\begin{itemize}
\item Datasets
  \begin{itemize}
  \item \verb=/DoubleElectron/Run2012A-13Jul2012-v1/AOD=
  \item \verb=/DoubleMu/Run2012A-13Jul2012-v1/AOD=
  \item \verb=/MuEG/Run2012A-13Jul2012-v1/AOD=
  \item \verb=/DoubleElectron/Run2012B-13Jul2012-v1/AOD=
  \item \verb=/DoubleMu/Run2012B-13Jul2012-v1/AOD=
  \item \verb=/MuEG/Run2012B-13Jul2012-v1/AOD=
  \item \verb=/DoubleElectron/Run2012C-PromptReco-v2/AOD=         
  \item \verb=/DoubleMu/Run2012C-PromptReco-v2/AOD=         
  \item \verb=/MuEG/Run2012C-PromptReco-v2/AOD=         
  \end{itemize}

\item Triggers
  \begin{itemize}
    \item \verb=HLT_Mu17_Mu8_v*=
    \item \verb=HLT_Mu17_Ele8_CaloIdT_CaloIsoVL_TrkIdVL_TrkIsoVL_v*=
    \item \verb=HLT_Mu8_Ele17_CaloIdT_CaloIsoVL_TrkIdVL_TrkIsoVL*=
    \item {\footnotesize \verb=HLT_Ele17_CaloIdT_CaloIsoVL_TrkIdVL_TrkIsoVL_Ele8_CaloIdT_CaloIsoVL_TrkIdVL_TrkIsoVL_v*=}
    \item \verb=HLT_Photon22_R9Id90_HE10_Iso40_EBOnly_v*=
    \item \verb=HLT_Photon36_R9Id90_HE10_Iso40_EBOnly_v*=
    \item \verb=HLT_Photon50_R9Id90_HE10_Iso40_EBOnly_v*=
    \item \verb=HLT_Photon75_R9Id90_HE10_Iso40_EBOnly_v*=
    \item \verb=HLT_Photon90_R9Id90_HE10_Iso40_EBOnly_v*=
  \end{itemize}
\end{itemize}
  
\begin{table}[htb]                                                                                                                                                              
\begin{center}                                                                                                                                                
\scriptsize
\caption{\label{tab:mcsamples} List of MC samples.}
\begin{tabular}{l|l|c}  
\hline
\hline
Process & Dataset Name & Cross Section [pb] \\
\hline
\zjets & \verb=/DYJetsToLL_M-50_TuneZ2Star_8TeV-madgraph-tarball/Summer12_DR53X-PU_S10_START53_V7A-v1/AODSIM=   & 3532.8 \\
\hline
\ttbar & \verb=/TTJets_MassiveBinDECAY_TuneZ2star_8TeV-madgraph-tauola/Summer12_DR53X-PU_S10_START53_V7A-v1/AODSIM= & 225.2 \\
\hline
ZZ & \verb=/ZZJetsTo4L_TuneZ2star_8TeV-madgraph-tauola/Summer12_DR53X-PU_S10_START53_V7A-v1/AODSIM=   & 0.1769 \\
& \verb=/ZZJetsTo2L2Q_TuneZ2star_8TeV-madgraph-tauola/Summer12_DR53X-PU_S10_START53_V7A-v1/AODSIM=     & 2.4487 \\
& \verb=/ZZJetsTo2L2Nu_TuneZ2star_8TeV-madgraph-tauola/Summer12_DR53X-PU_S10_START53_V7A-v3/AODSIM= & 0.3648 \\
\hline
WZ & \verb=/WZJetsTo3LNu_TuneZ2_8TeV-madgraph-tauola/Summer12_DR53X-PU_S10_START53_V7A-v1/AODSIM=    & 1.0575 \\
& \verb=/WZJetsTo2L2Q_TuneZ2star_8TeV-madgraph-tauola/Summer12_DR53X-PU_S10_START53_V7A-v1/AODSIM=     & 2.206 \\
\hline
WW & \verb=/WWJetsTo2L2Nu_TuneZ2star_8TeV-madgraph-tauola/Summer12_DR53X-PU_S10_START53_V7A-v1/AODSIM=    & 5.8123 \\
\hline
single top & \verb=/T_tW-channel-DR_TuneZ2star_8TeV-powheg-tauola/Summer12_DR53X-PU_S10_START53_V7A-v1/AODSIM= & 11.177 \\
           & \verb=/Tbar_tW-channel-DR_TuneZ2star_8TeV-powheg-tauola/Summer12_DR53X-PU_S10_START53_V7A-v1/AODSIM= & 11.177 \\
\hline
ttV & \verb=/TTZJets_8TeV-madgraph_v2/Summer12_DR53X-PU_S10_START53_V7A-v1/AODSIM=    & 0.208 \\
& \verb=/TTWJets_8TeV-madgraph/Summer12_DR53X-PU_S10_START53_V7A-v1/AODSIM=    & 0.232 \\
\hline
VVV & \verb=/ZZZNoGstarJets_8TeV-madgraph/Summer12_DR53X-PU_S10_START53_V7A-v1/AODSIM=    & 0.01922 \\
& \verb=/WWWJets_8TeV-madgraph/Summer12_DR53X-PU_S10_START53_V7A-v1/AODSIM=    & 0.08217 \\
& \verb=/WWZNoGstarJets_8TeV-madgraph/Summer12_DR53X-PU_S10_START53_V7A-v1/AODSIM=   & 0.0633 \\
%& \verb=/ZZZNoGstarJets_8TeV-madgraph/Summer12_DR53X-PU_S10_START53_V7A-v1/AODSIM=   & 0.01922 \\
\hline
\hline
\end{tabular}
\end{center}
\end{table}
