\documentclass{cmspaper}
\usepackage{color}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{slashbox}
\usepackage{epstopdf}  %added for MAC compiler
\usepackage{pdfpages}
\usepackage{lineno}
\usepackage{verbatim}
\usepackage{url}
\RequirePackage{lineno} 
%\RequirePackage{lineno} 

\usepackage{wrapfig}

%Note to authors: these definitions are suggested to be used for consistency
\newcommand{\pt}{$p_T$ }
\newcommand{\GeVc}{GeV/c}
\newcommand{\mll}{\ensuremath{M_{\ell\ell}}}
\newcommand{\z}{$Z$ }
\newcommand{\zjets}{$Z+\rm{jets}$ }
\newcommand{\gjets}{$\gamma+\rm{jets}$ }
\newcommand{\Z}{$Z$ } %redundancy can be good
\newcommand{\ttbar}{\ensuremath{t\bar{t}}}
\newcommand{\emu }{\ensuremath{e\mu}}
\newcommand{\ee  }{\ensuremath{ee}}
\newcommand{\eepm}{\ensuremath{e^+ e^-}}
\newcommand{\mm  }{\ensuremath{\mu\mu}}
\newcommand{\mmpm}{\ensuremath{\mu^+ \mu^-}}
\newcommand{\empm}{\ensuremath{e^\pm \mu^\mp}}
\newcommand{\ase}[2]{\ensuremath{_{~- #1}^{~+ #2}}}
\newcommand{\MET}{\ensuremath{\rm{E_{T}^{miss}}}}
\newcommand{\met}{\mbox{$\raisebox{.3ex}{$\not$}E_T$\hspace*{0.5ex}}} 
\newcommand{\effr}{$R_{e\mu}$} %used to be \epsilon
\newcommand{\effrm}{$R_{\mu e}$} %used to be \epsilon
\newcommand{\sta}{$\sigma\times A$} %notation is such that A includes BR
\newcommand{\statistics}{CL$_\mathrm{S}$}
\newcommand{\njets}{$N_{\rm{jets}}$}

%The lumi so that if it changes it's easier to update
\newcommand{\lumi}{9.2~fb$^{-1}$}

%loose(tight) signal region met cut
\newcommand{\signalmetl}{100}
\newcommand{\signalmett}{200}
\newcommand{\signalmetvt}{300}

\newcommand{\resulttitle}
%{                       &   MET $>30$  GeV    &   MET $>60$  GeV    &   MET $>100$ GeV    &   MET $>200$ GeV \\}
%{                       &   MET $>30$  GeV    &   MET $>60$  GeV    &   MET $>100$ GeV    &   MET $>200$ GeV  &  MET $>300$ GeV  \\}
%move 300 to 150
{                       &   MET $>30$  GeV    &   MET $>60$  GeV    &   MET $>100$ GeV    &   MET $>150$ GeV  &  MET $>200$ GeV  \\}

\newcommand{\wjets}{$\rm{W}+{\rm jets}$}
\newcommand{\zzmet}{$\rm{ZZ}+\MET$}
\newcommand{\wzmet}{$\rm{WZ}+\MET$}
\newcommand{\wzzmet}{$\rm{WZ/ZZ}+\MET$}
\newcommand{\Ht}{$H_{T}$}
\newcommand{\cls}  {\ensuremath{\mathrm{CL_S}}}


\begin{document}


%\begin{comment}

\begin{titlepage}

  %\internalnote{2011/000}
  \cmsnote{2011/254}

  \date{\today}
 
  \title{Searches for beyond-the-standard model physics in events with a Z boson, jets and missing transverse energy}

  %No Victor this time (sorry, Victor)
  \begin{Authlist}
    D.~Barge, C.~Campagnari, D.~Kovalskyi, V.~Krutelyov
    \Instfoot{ucsb}{University of California, Santa Barbara, USA}

    W.~Andrews, G.~Cerati, D.~Evans, F.~Golf, I.~MacNeill, S.~Padhi, Y.~Tu, F.~W\"urthwein, 
	A.~Yagil, J.~Yoo
    \Instfoot{ucsd}{University of California, San Diego, USA}

	L.~Bauerdick, K.~Burkett, I.~Fisk, Y.~Gao, O.~Gutsche, B.~Hooberman, S.~Jindariani, J.~Linacre, V.~Martinez Outschoorn
    \Instfoot{fnal}{Fermi National Accelerator Laboratory, Batavia, Illinois, USA}
  \end{Authlist}

  \begin{abstract}

This note describes a search for beyond-the-standard model (BSM) physics in events with a leptonically-decaying Z boson, 
jets, and missing transverse energy (\MET).
This signature is predicted to occur in several BSM scenarios, for example supersymmetric (SUSY) models.
Two search strategies are pursued. The first is an inclusive approach which selects events with at least two jets and
large \MET, produced in association with the Z$\to\ell\ell$ candidate. The second is a targeted search 
in which additional requirements are imposed in order to achieve sensitivity to the production of the weakly-coupled
SUSY charginos and neutralinos. The main backgrounds of SM \zjets\ and \ttbar\ production are estimated with the data-driven 
\MET templates technique and the opposite-flavor subtraction technique, respectively
Additional backgrounds are estimated from simulation after validation in data control samples. 
Good agreement is observed between the data and the predicted background in low \MET\ control regions, which validates the
background estimation methodology. The results in the signal regions, defined by the requirement \MET\ $>$ 100 GeV, will be
unblinded soon. These results will be interpreted in the context of simplified model spectra.

\end{abstract}

\end{titlepage}

%\end{comment}

\setcounter{page}{2}%JPP


\newpage
\tableofcontents

\newpage
\linenumbers
\input{changes.tex}
\input{introduction.tex}
\input{datasets.tex}
\input{eventsel.tex}
\input{yields.tex}
\input{bkg.tex}
\input{results.tex} 
\input{optimization.tex} 
\input{interpretation.tex} 
\input{summary.tex}
%\input{sigregion.tex}
%\input{systematics.tex}
%\input{SMS}
%\input{outreach}


\clearpage
\input{bibliography.tex}

\appendix
\input{appendix_edge.tex}
\input{appendix_results.tex}
\input{appendix_templates.tex}

\end{document}
