\begin{thebibliography}{10}
%  \bibitem {NOTE000} {\bf CMS Note 2005/000},
%    X.Somebody et al.,
%    {\em "CMS Note Template"}.

%\bibitem{ref:Ztemplates} ADD REF TO MET TEMPLATES NOTE, WHEN AVAILABLE

\bibitem{ref:osnote} CMS AN-2010/370

\bibitem{ref:ospaper} arXiv:1103.1348v1 [hep-ex], ``Search for Physics Beyond the Standard Model in Opposite-Sign Dilepton Events at $\sqrt{s} = 7$~TeV.''

\bibitem{ref:top} Phys.Lett.B695:424-443,2011 

\bibitem{ref:vbtf} https://twiki.cern.ch/twiki/bin/viewauth/CMS/SimpleCutBasedEleID

\bibitem{ref:conv} D.~Barge {\em at al.}, AN-CMS2009/159.

\bibitem{ref:HWW} CMS AN-2011/155

\bibitem{ref:xsec} https://twiki.cern.ch/twiki/bin/view/CMS/ProductionReProcessingSpring10 
% {\color{red} Is this the right reference?}

\bibitem{ref:victory}V.~Pavlunin, Phys. Rev. {\bf D81}, 035005 (2010).

\bibitem{ref:ourvictory}  D.~Barge {\em at al.}, AN-CMS2009/130.

\bibitem{ref:dy} W.~Andrews {\em et al.}, AN-CMS2009/023.

\bibitem{ref:FR} D.~Barge {\em at al.}, AN-CMS2010/257.

\bibitem{ref:evans}W.~Andrews {\em et al.}, AN-CMS2010/274.

\bibitem{ref:bayes.f} J.~Conway, {\tt http://www-cdf.fnal.gov/physics/statistics/code/bayes.f}.

\bibitem{ref:cl95cms} G.~Landsberg, {\tt https://twiki.cern.ch/twiki/pub/CMS/EXOTICA/cl95cms.c}

\bibitem{ref:scan} {\tt https://hypernews.cern.ch/HyperNews/CMS/get/susy/617/2/1.html}

\bibitem{ref:sanjay} {\tt https://twiki.cern.ch/twiki/bin/view/CMS/SUSY38XSUSYScan}

\bibitem{ref:pdf} arXiv:hep-ph/0605240v2

\bibitem{ref:lumi}
{CMS Collaboration}, ``Measurement of CMS luminosity'', {\em CMS-PAS} {\bf
  EWK-10-004} (2010).

\bibitem{ref:smooth} {\tt CleanExclusion.cc} available at
{\tt https://twiki.cern.ch/twiki/bin/viewauth/CMS/SUSYLimitTools}

\bibitem{ref:cousins} R.~Cousins, {\tt http://www.physics.ucla.edu/\~cousins/stats/cousins\_lognormal\_prior.pdf}

\bibitem{ref:harper} S.~Harper, private communication (relayed to us by M.~Chiorboli.).

\bibitem{ref:MT2} A. Barr {\em at al.}, J.Phys.G29:2343-2363,2003;
Cheng, H.C., Han, arXiv:hep-ph/0810.5178v2.\\
{\tt http://indico.cern.ch/contributionDisplay.py?contribId=3\&confId=66410}

\bibitem{ref:MT2J} {\tt http://indico.cern.ch/contributionDisplay.py?contribId=5\&confId=93837}

\bibitem{ref:brown} M.~Narain {\em et al.}, CMS AN-2010/259; we thank the 
Brown group for providing their code to us.


    
\end{thebibliography}
