\section{Model Dependent Upper Limits}
\label{sec:sigmalimit}

As an example of how the upper limit presented in Sec.~\ref{sec:limits} can be
used to test if a specific model is excluded, in this section we consider the benchmark
SUSY processes LM1, LM3 and LM6.
We place upper limits on the quantity $\sigma \times A$,
assuming efficiencies and uncertainties from these processes, and compare them to 
the expected values of $\sigma \times A$.
Here $\sigma$ is the signal production cross section and $A$ is the signal acceptance.

The signal event yield $N_{SIG}$ can be expressed as:

\begin{equation}
N_{SIG} = \sigma \times A \times \epsilon \times \mathcal{L},
\end{equation}

and we therefore have:

\begin{equation}
N_{SIG}/( \epsilon \times \mathcal{L}) = \sigma \times A.
\end{equation}

Here  $\epsilon$ is the signal efficiency and $\mathcal{L}$ is the integrated luminosity. 
Since we wish to place an upper limit on the quantity $\sigma \times A$, we must evaluate
the quantity $N_{SIG}/(\epsilon \times \mathcal{L})$.  Because of the efficiency
in the denominator, this upper limit cannot be calculated in an entirely model-independent
way; rather, it must be calculated with respect to a specific model. We therefore evaluate
the upper limit on $\sigma \times A$ with respect to LM1, LM3 and LM6.  
For each process, we must calculate both the efficiency and its uncertainty.

We evaluate the signal efficiencies and acceptances using MC. The acceptance is defined by he
following requirements which are applied on the generator-level quantities:

\begin{itemize}
\item 2 electrons or muons with \pt\ $>$ 10 GeV and $|\eta|<2.5$, at least 1 lepton must have \pt\ $>$ 20 GeV
\item Opposite-sign pair, veto same-flavor pairs with $76 < \rm{m(\ell\ell)} < 106$~GeV
\item Count genjets with $p_T > 30$~GeV, $|\eta|<3.0$, $\Delta R > 0.4$ from any selected lepton as defined above, require at least 2 genjets
\item $H_{T}^{gen}$ is the scalar sum of selected genjet \pt's, $MET^{gen}$ is the event gen-level missing ET, and $y^{GEN} \equiv MET^{gen}/\sqrt{H_{T}^{gen}}$.
\end{itemize}

For the 2010, high \met, and high \Ht\ signal regions, we add the corresponding
requirements on the generator-level quantities $H_{T}^{gen}$, $MET^{gen}$ and $y^{GEN}$.
The signal efficiency is defined as the fraction of events passing the above acceptance requirements, which
also pass the full reco-level selection. The efficiency uncertainty is determined by the trigger uncertainty (2\%),
the lepton selection uncertainty (2\%/lepton) and the hadronic energy scale uncertainties quoted in Table~\ref{tab:jetmet}.

Armed with the efficiencies and uncertainties calculated in the previous 2 sections, we proceed
to calculate upper limits on the quantity $\sigma \times A$ for the 3 benchmark SUSY 
scenarios. We calculate Bayesian 95\% CL upper
limits using the cl95cms software, assuming a log-normal model of nuissance parameter integration.
We quote here the upper limits from the high \Ht\ signal region.
The results are summarized in
Table~\ref{tab:models}. These results show that the LM1, LM3 and LM6 scenarios are excluded.

\begin{table}[hbt]
\begin{center}
\caption{\label{tab:models} Summary of model-dependent limits. The efficiency and acceptance are
defined in the text; the efficiency uncertainty is dominated by the uncertainty in the hadronic
energy scale. The 95\% CL Bayesian UL on the quantity $\sigma\times A$ is indicated, as well as
the value of this quantity for the LM1, LM3 and LM6 scenarios.}
\begin{tabular}{l|ccc}
\hline
                                         & LM1              & LM3             & LM6               \\
\hline
\hline
{\bf 2010 signal region}                 &                  &                 &                   \\
\hline
efficiency (\%)                          &  50 $\pm$ 5      & 46 $\pm$ 5      & 52 $\pm$ 4        \\
acceptance (\%)                          &  2.0             & 1.2             & 3.5               \\
UL($\sigma \times A$) (fb)               &  47              & 51              & 44                \\
$\sigma \times A$ (fb)                   &  140             & 60              & 16                \\
\hline
\hline
{\bf high \met\ signal region}           &                  &                 &                   \\
\hline
efficiency (\%)                          &  46 $\pm$ 10     & 43 $\pm$ 12     & 54 $\pm$ 6        \\
acceptance (\%)                          &  1.3             & 0.67            & 2.8               \\
UL($\sigma \times A$) (fb)               &  26              & 29              & 21                \\
$\sigma \times A$ (fb)                   &  87              & 35              & 13                \\
\hline
\hline
{\bf high \Ht\ signal region}            &                  &                 &                   \\
\hline
efficiency (\%)                          &  42 $\pm$ 13     & 40 $\pm$ 13     & 52 $\pm$ 7        \\
acceptance (\%)                          &  0.94            & 0.67            & 2.5               \\
UL($\sigma \times A$) (fb)               &  16              & 18              & 12                \\
$\sigma \times A$ (fb)                   &  68              & 36              & 12                \\
\hline
\end{tabular}
\end{center}
\end{table}






\begin{comment}
-----------------------------------------------

LM1 2010    sigma X acc   0.26
LM1 highmet sigma X acc   0.17
LM1 highht  sigma X acc   0.13

LM3 2010    sigma X acc   0.11
LM3 highmet sigma X acc   0.062
LM3 highht  sigma X acc   0.064

LM6 2010    sigma X acc   0.029
LM6 highmet sigma X acc   0.024
LM6 highht  sigma X acc   0.022


LM1 2010    0.047
LM1 highmet 0.026
LM1 highht  0.016

LM3 2010    0.051
LM3 highmet 0.029
LM3 highht  0.018

LM6 2010    0.044
LM6 highmet 0.021
LM6 highht  0.012


LM1

N(gen)           114514
pre-filter:      219190

N(acc)  2010     4369
N(reco) 2010     2181
acceptance 0.038 efficiency 0.50

N(acc)  high MET 2692
N(reco) high MET 1243
acceptance 0.024 efficiency 0.46

N(acc)  high HT  2108
N(reco) high HT  895
acceptance 0.018 efficiency 0.42

-----------------------------------------------

LM3

N(gen)           123627
pre-filter       220000

N(acc)  2010     2615
N(reco) 2010     1201
acceptance 0.021 efficiency 0.46

N(acc)  high MET 1513
N(reco) high MET 649
acceptance 0.012 efficiency 0.43

N(acc)  high HT  1504
N(reco) high HT  598
acceptance 0.012 efficiency 0.40

-----------------------------------------------

LM6

N(gen)           121523
pre-filter       220000

N(acc)  2010     7622
N(reco) 2010     3959
acceptance 0.063 efficiency 0.52

N(acc)  high MET 6150
N(reco) high MET 3295
acceptance 0.051 efficiency 0.54

N(acc)  high HT  5453
N(reco) high HT  2856
acceptance 0.045 efficiency 0.52

-----------------------------------------------
\end{comment}
